\documentclass[11pt]{article}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{lastpage}

\setlength{\textheight}{9in} \setlength{\headheight}{.2in}
\setlength{\headsep}{0.3in} \setlength{\topmargin}{0in}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}

\lhead{Name\underline{\hspace{2in}}}
\rfoot{Page \thepage \ of \pageref{LastPage}}

\begin{document}
	\begin{center}
		MATH-110: Calculus I\\
		Fall 2016\\
		Siena College\\
		\vspace{.1in}
		Test 1
	\end{center}
	\vspace{.1in}
	
	For each question I would like you to show and explain each question and how you solve it.  It is a very important skill to be able to communicate your thoughts and ideas in an understandable way. When reading your work I would like to know what you were thinking when soling the problem.\\
	
	I'd recommend looking at all the questions first so you can think about them while solving other problems.\\
	
	For problems 1-4 do the following and explain your reasoning.  (Answer {\bf Why?}) (20 points each)
	\begin{enumerate}[a)]
		\item  Identify the {\bf Domain} (1 point)
		\item  Identify the {\bf Range} (1 point)
		\item  Identify any {\bf Zeros} (1 point)
		\item  Identify the intervals where the function is {\bf One-to-One (1-1)} (2 points)
		\item  Identify any {\bf Vertical Asymptotes} (4 points) and for each:
		\begin{enumerate}[i)]
			\item  Find the Left Limit
			\item  Find the Right Limit
			\item  Find the Normal Limit
		\end{enumerate}
		\item  Identify any {\bf Horizontal Asymptotes} (4 points)
		\item  Identify any {\bf Slant Asymptotes} (bonus 2 points if it exists)
		\item  Identify on what intervals the function is {\bf Continuous} (3 points)
		\item  Make a {\bf Sketch} (4 points)
	\end{enumerate}
	\newpage
	\begin{enumerate}
		\item  $$f_{\number\value{enumi}}(x) = \frac{(x-8)(x-4)(x+4)}{(x-7)(x-2)}$$
		\newpage
		\item  $$f_{\number\value{enumi}}(x) = \frac{(x-8)^2(x+6)}{(x-6)^2(x-4)}$$
		\newpage
		\item  $$f_{\number\value{enumi}}(x) = \frac{(x+2)}{(x-5)(x-4)^2(x+10)^3}$$
		\newpage
		\item  $$f_{\number\value{enumi}}(x) = \frac{e^x}{x^4}$$
		\newpage
		\item Intermediate Value Theorem: (10 points each)\par
		For each question below answer the following questions and explain:\\
		Is this True or False?  Are there any assumptions need to be made?\par
		You might need to think a bit about these.\\
		Hint: They are both True with the right assumptions.
		\begin{enumerate}[i)]
			\item  Throughout my day I travel a lot, from home to Siena, back home, etc...  Assuming that I start my day laying in my bed and end the day laying in my bed it is guaranteed that at some point in my day my head will be at the exact same elevation as it was initially.
			\vspace{2.5in}
			\item  My friend told me that if you have a table with 4 legs and it's wobbly I can just rotate the table and at some point it won't wobble any more.\\
			(https://www.mathsisfun.com/algebra/intermediate-value-theorem.html)
		\end{enumerate}
		\newpage
		\item Bonus Question (2 points each)
		\begin{enumerate}[i)]
			\item  What was the bonus question we came up with in class on Wednesday, September 21, 2016?
			\vspace{2in}
			\item  What was the answer?
		\end{enumerate}
	\end{enumerate}
	%\vbox{\noindent {\bf Problem 1 (a):} \\
	%\begin{align*}
	%\end{align*}
	%}
	
\end{document}
